Page not found

### 2023-06-19 manuscript/chapters/2_neural_fields.qmd
*clicks* noice

We should however note that the results obtained in @sec-fixedpoints are valid in the $N \to \infty$ limit. A numerical analysis shows in @fig-spectrum that already at $N=64$, the analytic eigenvalues match the numerical eigenvalues closely, and this correspondence improves when we take larger $N$ (typically we will for the rest of this thesis take $N > 10^3$).

```{python}
#| label: fig-spectrum
#| fig-cap: Spectrum of $K$ for $N=64$ and $p=2$. The numerical estimation (black) of the eigenvalues is close to the analytical ($N \to \infty$) derivation (red). Eigenvalues above the dotted gray line(positive values) correspond to unstable fixed points, and below (negative values) correspond to stable fixed points. Only the 
#| fig-subcap:
#|   - Pattern (stable) fixed point
#|   - Zero (unstable) fixed point
#| layout-ncol: 2
#| echo: false

@@

def plot_spectrum(hstar_str: str):
	params = LowRankRNNParams.new_valentin(p=2, N=256, phi=sigmoid, I_ext=zero, exclude_self_connections=False)
	if hstar_str == 'pattern':
		hstar = params.F[:, 0]
	elif hstar_str == 'zero':
		hstar = np.zeros(params.N)
	dphi = dsigmoid(hstar)
	l = 1/params.N * np.einsum('im,im->m', params.F, params.G * dphi[:, None]) - 1
	l.sort()
	J = np.einsum('im,jm->ij', params.F, params.G * dphi[:, None]) / params.N - np.eye(params.N)

	fig, ax = plt.subplots()
	mktrans(fig, ax)
	ax.axhline(0, color='gray', linestyle='--')
	ax.plot(np.sort(np.linalg.eigvals(J).real)[::-1][:8], marker='o', clip_on=False)
	ax.plot([7,8,8.5], np.sort(np.linalg.eigvals(J).real)[::-1][8:11], linestyle='--', color='k', clip_on=False)
	ax.plot(l[::-1], color='r', marker='o', clip_on=False)
	ax.set_ylim((-1, 0.5))
	ax.set_xlim((0, 8.5))
	ax.set_ylabel('Eigenvalues')
	breathe()
	return fig, ax

@@

::: {.content-visible when-format="html"}
![(TODO remove overlap, change notation, color for activity) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/embedding_d=1_h0=0_phi=sigmoid.mp4){width=400px #fig-p1}
:::

::: {.content-visible when-format="pdf"}
![(TODO PDF remove overlap, change notation, color for activity) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level.](figures/lol7.jpg){width=400px #fig-p1}
:::

@@

## A cycling neural field {#sec-cyling-nf}

>>>>

We should however note that the results obtained in @sec-fixedpoints are valid in the $N \to \infty$ limit. A numerical analysis shows in @fig-spectrum that at $N=250$, the numerical eigenvalues approximate the analytical eigenvalues, and this correspondence improves when we take larger $N$ (typically we will for the rest of this thesis take $N > 10^3$).

```{python}
#| label: fig-spectrum
#| fig-cap: Spectrum of $K$ for $N=250$ and $p=2$. The numerical estimation (black, eigenvalues $\lambda_\mu$ and $\lambda_\perp=-1$) of the eigenvalues is close to the analytical ($N \to \infty$) derivation (red, only eigenvalues $\lambda_\mu$). Eigenvalues above the dotted gray line (positive values) correspond to unstable fixed points, and below (negative values) correspond to stable fixed points.
#| fig-subcap:
#|   - Pattern (stable) fixed point
#|   - Zero (unstable) fixed point
#| layout-ncol: 2
#| echo: false

@@

def plot_spectrum(hstar_str: str):
	params = LowRankRNNParams.new_valentin(p=2, N=250, phi=sigmoid, I_ext=zero, exclude_self_connections=False)
	if hstar_str == 'pattern': hstar = params.F[:, 0]
	elif hstar_str == 'zero': hstar = np.zeros(params.N)
	dphi = dsigmoid(hstar)
	J = np.einsum('im,jm->ij', params.F, params.G * dphi[:, None]) / params.N - np.eye(params.N)
	eig_num = np.sort(np.linalg.eigvals(J).real)[::-1]
	eig_ana = { 'zero': 0.19061, 'pattern': -0.28090 }[hstar_str]  # see appendix A

	fig, ax = plt.subplots()
	mktrans(fig, ax)
	ax.axhline(0, color='gray', linestyle='--')
	ax.plot(eig_num[:8], marker='o', clip_on=False)
	ax.plot([7,8,8.5], eig_num[8:11], linestyle='--', color='k', clip_on=False)
	ax.plot(np.arange(params.p), np.full(params.p, eig_ana), color='r', marker='o', clip_on=False)
	ax.set_ylim((-1, 0.5))
	ax.set_xlim((0, 8.5))
	ax.set_ylabel('Eigenvalues')
	ax.set_xlabel('nth eigenvalue')
	breathe()
	return fig, ax

# %matplotlib inline

@@

::: {.content-visible when-format="html"}
![Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level, and the colorbar doubles as a y-axis.](figures/embedding_d=1.mp4){#fig-p1}
:::

::: {.content-visible when-format="pdf"}
![(TODO) Simulation of the Gaussian network of neurons with $p=1$. Every neuron is represented by a dot, of which the height represents its activity level, and the colorbar doubles as a y-axis.](figures/lol7.jpg){#fig-p1}
:::

@@

## A cycling neural field {#sec-cycling-nf}

### 2023-06-19 manuscript/chapters/3_mappings.qmd
*clicks* noice

![Non-injectivity of $S^{-1}$ means that two segment populations can refer to the same square population.](figures/photo_2023-06-12_00-46-26.jpg){#fig-non-injection}

@@

Research in computer science and efficient data structures has given rise to other ways of storing 2-dimensional information in a 1-dimensional memory.
A problem in GPU computing is that of texture locality: sampling textures often involves reading data corresponding to a small 2D region, and therefore to improve speed (minimize cache misses), the 2D data should be packed close together in the 1D memory.
One way of ordering the 2D texture data in the 1D memory is by using the Z-order curve (also known as "Morton mapping", and similar to the "Lebesgue curve" @Sagan1994). In this way, points close in 1D *tend* to be tightly packed in 2D. We can define the Z-order curve (Z-mapping) in the following way:[^zcurve]

@@

![(TODO) Averaging $2^n$ of the $4^n$ segments populations of $S^n$ results in the $2^n = 4^{n/2}$ segments populations of $S^{n/2}$](figures/photo_2023-06-13_12-15-32.jpg){width=400px #fig-averaging}

>>>>

<!-- ![Non-injectivity of $S^{-1}$ means that two segment populations can refer to the same square population.](figures/photo_2023-06-12_00-46-26.jpg){#fig-non-injection}

Nicole: removed. too confusing
-->

@@

Research in computer science and efficient data structures has given rise to other ways of storing 2-dimensional information in a 1-dimensional memory.
A problem in GPU computing is that of texture locality: sampling textures often involves reading data corresponding to a small 2D region, and therefore to improve speed (minimize cache misses), the 2D data should be packed close together in the 1D memory.
One way of ordering the 2D texture data in the 1D memory is by using the Z-order curve (also known as "Morton mapping", and similar to the "Lebesgue curve" @sagan_space-filling_1994, chapter 6). In this way, points close in 1D *tend* to be tightly packed in 2D. We can define the Z-order curve (Z-mapping) in the following way:[^zcurve]

@@

![(TODO) Averaging $2^n$ of the $4^n$ segments populations of $S^n$ results in the $2^n$ segments populations](figures/photo_2023-06-13_12-15-32.jpg){width=400px #fig-averaging}

### 2023-06-19 manuscript/chapters/4_locality.qmd
*clicks* noice

Nicole: let's not mention Netto's theorem here. It applies to S^{-1}, and it becomes difficult to reason about when we talk about S. I don't think the proof works strictly in our case, because the Z-mapping is not a bijection, but let us assume uwuwuwu
-->

@@

and that in @sec-cyling-nf, numerical simulations showed that $I^\text{rec}_U(\vec v)$ is a well-behaved function.

>>>>

Nicole: let's not mention Netto's theorem here. It applies to S^{-1}, and it becomes difficult to reason about when we talk about S. I don't think the proof works strictly in our case, because the Z-mapping is not a bijection, but let us assume uwuwuwu

Nicole again: our Z-mapping is not defined in the same way as the Lebesgue curve, because we use indicator functions to take bit representations. We are stepwise functions. Our Z-mapping is a bijection, and not continuous.
-->

@@

and that in @sec-cycling-nf, numerical simulations showed that $I^\text{rec}_U(\vec v)$ is a well-behaved function.

### 2023-06-19 manuscript/chapters/5_conclusion.qmd
*clicks* noice

In this thesis, we have constructed an example of neural field dynamics in $\R^2$, that can be mapped to a neural field equation in $[0,1]$, via well-known mappings (such as the Z-curve) between $[0,1]^2$ and $[0,1]$. To illustrate this, we have introduced a coarse-graining procedure in which numerical simulations of $2^n$ segment populations in $[0,1]$ converge to the same dynamics obtained from simulations of $4^n$ square populations in $[0,1]^2$. Additionally, we showed that the reduction of dimensionality using the mappings can be repeated, even if the starting neural field has a fractal structure. To help quantify how the mapping conserves the regularity between neural fields, we introduced a measure of locality, based on "average variation". Locality guarantees that the neural field equation on $[0,1]$ can be numerically approximated using classical grid-based methods.

>>>>

In this thesis, we have constructed an example of neural field dynamics in $\R^2$, that can be mapped to a neural field equation in $[0,1]$, via well-known measurable bijections (such as the Z-mapping) between $[0,1]^2$ and $[0,1]$. To illustrate this, we have introduced a *coarse-graining* procedure in which numerical simulations of $2^n$ segment populations in $[0,1]$ converge to the same dynamics obtained from simulations of $4^n$ square populations in $[0,1]^2$. Additionally, we showed that the reduction of dimensionality using the mappings can be repeated, even if the starting neural field has a fractal structure. To help quantify how the mapping conserves the regularity between neural fields, we introduced a *measure of locality*, based on "average variation". Locality guarantees that the neural field equation on $[0,1]$ can be numerically approximated using classical grid-based methods.
